Regression Cube Analysis of Cohort Study Data

### 2015-06-20 draft.tex
added limitations for CFS

The number of features calculated by the CFS algorithm is dependent on the information entropy in the data.
%%
In our epidemiological data, we usually observed a number of 10 to 30 features.
%%
The number of selected features using the CFS algorithm reflects their information entropy on the target.
%%
A large list of features is an expression of low correlation to the target feature.
%%

@@

\paragraph{3D (Cube) View.}
%%
Introducing $Z$ creates a 3D \emph{Regression Cube} (Fig.~\ref{fig:Cube}b).
%%
\add{The selected metric (per default set to $R^2$)} of each cube entry (\emph{voxel}) are mapped to opacity to reduce the overlap.
%%
\magenta{Object size is not used to encode information because it would result in a cluttered view.}
%%
\design{
%%
Epidemiologists with background on statistics argued, that the visualization of descriptive metrics derived from different regression methods (e.g., $Z \sim X + Y$) is misleading, as they can be compared relatively, but not in precise numbers.
%%
Therefore, we decided to map metrics of different regression methods on distinct colors (i.e., orange for linear regression and blue for logistic regression).
%%
}
%%
%The visualization of descriptive metrics derived from different regression cubes (e.g., $Z \sim X + Y$) is misleading, as they can be compared relatively, but not in precise numbers.
%%
%Therefore, the $R^2$ results of different regression methods are encoded using different colors (i.e., orange for linear regression and blue for logistic regression).
%%
Thus, the cube can be easily extended using other regression types.
%%
For cubes with a fixed target feature, e.g., $Cancer \sim X + Y + Z$, no such encodings are required and the $z$ dimension can be compared directly.
%%
\\\\
%%
Our goal is to create an overview visualization for a data set.
%%
We also want to incorporate expert knowledge into the visualization by adapting the underlying formulas.
%%
These two approaches do not exclude each other, they rather underline the difference in purpose of the chosen formula.
%%
The different analysis approaches require different starting points using the \emph{Regression Cube}.

@@

>>>>

The number of features calculated by the CFS algorithm is dependent on the information entropy in the data.
%%
In our epidemiological data, we usually observed a number of 10 to 30 features.
%%
The number of selected features using the CFS algorithm reflects their information entropy on the target.
%%
A large list of features is an expression of low correlation to the target feature.
%%
\magenta{
The tradeoff of the CFS algorithm is the potential removal of features of interest for the domain expert.
%%
This problem is handled in the next subsection as part of the 3D representation of the regression results.
}
%%

@@

\paragraph{3D (Cube) View.}
%%
Introducing $Z$ creates a 3D \emph{Regression Cube} (Fig.~\ref{fig:Cube}b).
%%
\add{The selected metric (per default set to $R^2$)} of each cube entry (\emph{voxel}) are mapped to opacity to reduce the overlap.
%%
\magenta{Object size is not used to encode information because it would result in a cluttered view.}
%%
\design{
%%
Epidemiologists with background on statistics argued, that the visualization of descriptive metrics derived from different regression methods (e.g., $Z \sim X + Y$) is misleading, as they can be compared relatively, but not in precise numbers.
%%
Therefore, we decided to map metrics of different regression methods on distinct colors (i.e., orange for linear regression and blue for logistic regression).
%%
}
%%
%The visualization of descriptive metrics derived from different regression cubes (e.g., $Z \sim X + Y$) is misleading, as they can be compared relatively, but not in precise numbers.
%%
%Therefore, the $R^2$ results of different regression methods are encoded using different colors (i.e., orange for linear regression and blue for logistic regression).
%%
Thus, the cube can be easily extended using other regression types.
%%
For cubes with a fixed target feature, e.g., $Cancer \sim X + Y + Z$, no such encodings are required and the $z$ dimension can be compared directly.
%%
\magenta{
As mentioned previously, the dimension reduction using the CFS algorithm potentially removes features, which are of interest for the domain expert.
%%
To tackle this problem, the $z$ dimension of the cube contains all features of the data set, allowing to assess their influence on the models.
%%
The $x$ and $y$ dimensions are restricted to the features extracted from the CFS algorithm.
}
%%
\\\\
%%
Our goal is to create an overview visualization for a data set.
%%
We also want to incorporate expert knowledge into the visualization by adapting the underlying formulas.
%%
These two approaches do not exclude each other, they rather underline the difference in purpose of the chosen formula.
%%
The different analysis approaches require different starting points using the \emph{Regression Cube}.

@@

\magenta{Using a check-box, the user can disable the CFS preprocessing step, which is useful for small data sets, where the user does not want to reduce the number of features.}
